---
title: "powerAppResearch"
author: "Damyenn Cardenas"
date: "2023-06-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Testing Structure

The way items will be getting tested is

-   speed using 'profvis'
-   time between idles using 'reactlog' and 'profvis'

# Organization of Data

I will be organizing data into different levels. Each of these levels will be based on how much time and speed was changed for each individual change.

### Branch defaultWRLog

This branch is a first look at what **reactlog** can provide and how I plan to write and take information moving forward

First attempt is a Markdown table writing down time each plot renders and when the app first enter idle (When it loads for the user)

-   **Side note:** CPU scheduling information is perfect for describing and organizing data

-   Arrival Time: Time the process arrives in ready queue

-   Completion Time: Time process completes its execution

-   Burst Time: Time required by a plot to finish **Might not work for this organization**

-   Turn around time: How long to perform that process *(difference between completion and arrival time)*

-   Waiting Time: Time spend in the waiting process *(difference turn around time and burst time)* **Might not work for this organization**

```{r}
library(shiny)
library(reactlog)

reactlog_enable()

runApp("powerApp")

reactlogShow()

reactlogReset()

```

| Plot                | Arrival Time | Completion Time | Turn Around Time | Waiting Time | Connections |
|------------|------------|------------|------------|------------|------------|
| Pdist               | 0s           | 0.3246s         | 0.3246s          |              | 7           |
| Cohen               | 0.3254s      | 0.3571s         | 0.0317s          |              | 7           |
| Tdist               | 0.3576s      | 0.3910s         | 0.0334s          |              | 7           |
| First Idle Position | 0s           | 0.3915s         | 0.3915s          |              |             |

```{r}
library(shiny)
library(profvis)

profvis({
  runApp("powerApp")
})

```

Second attempt is using a new package called profvis. This tool is used for profiling and will be the direction I go moving forward

**You can rename the extension of the saved profiling files into html files. This can be helpful when it comes to presentation and just general info**

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| Pdist       | 300ms        | 490ms           | 180ms            |
| Cohen       | 520ms        | 530ms           | 10ms             |
| Tdist       | 540ms        | 550ms           | 10ms             |
| First Idle? | 0ms          | 550ms           | 550ms            |

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| Pdist       | 300ms        | 510ms           | 200ms            |
| Cohen       | 520ms        | 530ms           | 10ms             |
| Tdist       | 530ms        | 560ms           | 30ms             |
| First Idle? | 0ms          | 560ms           | 560ms            |

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| Pdist       | 300ms        | 490ms           | 190ms            |
| Cohen       | 500ms        | 510ms           | 10ms             |
| Tdist       | 520ms        | 530ms           | 10ms             |
| First Idle? | 0ms          | 550ms           | 550ms            |

These tables show the app starting without any changes and without any interaction. As you can see the Pdist plot takes the longest as the others already done very quickly

Now I am going to mess with the different sliders to see what changes with each one. Which graph updates and how long it takes.

The first slider is: **Cohen's D**

```{r}
library(shiny)
library(profvis)

profvis({
  runApp("powerApp")
})

```

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| 1st Pdist   | 310ms        | 560ms           | 240ms            |
| 1st Cohen   | 570ms        | 580ms           | 10ms             |
| 1st Tdist   | 590ms        | 600ms           | 10ms             |
| 2st Pdist   | 1660ms       | 1880ms          | 240ms            |
| 2st Cohen   | 0ms          | 0ms             | 0ms              |
| 2st Tdist   | 1900ms       | 1920ms          | 20ms             |
| First Idle  | 0ms          | 600ms           | 600ms            |
| Second Idle | 1650ms       | 1920ms          | 270ms            |

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| 1st Pdist   |              |                 |                  |
| 1st Cohen   |              |                 |                  |
| 1st Tdist   |              |                 |                  |
| 2st Pdist   |              |                 |                  |
| 2st Cohen   |              |                 |                  |
| 2st Tdist   |              |                 |                  |
| First Idle  |              |                 |                  |
| Second Idle |              |                 |                  |

| Plot        | Arrival Time | Completion Time | Turn Around Time |
|-------------|--------------|-----------------|------------------|
| 1st Pdist   |              |                 |                  |
| 1st Cohen   |              |                 |                  |
| 1st Tdist   |              |                 |                  |
| 2st Pdist   |              |                 |                  |
| 2st Cohen   |              |                 |                  |
| 2st Tdist   |              |                 |                  |
| First Idle  |              |                 |                  |
| Second Idle |              |                 |                  |
